Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-18 paper.tex
minor changes to section 7

As already mentioned in section \ref{sec:model}, problems that are not directly related to code correctness may be tackled with formal methods, as long as the are conveniently modeled. Ara\'ujo {\it et. al} \cite{Araujo16} employed SMT for handling non-convex optimization problems, with the goal of ensuring optimal solutions. Indeed, it is possible to recursively re-constrains a model checking procedure, by using the current counterexample as a seed for the next run, until a global minimum is achieved. Nonetheless, the elapsed execution time is still a bottleneck for some applications, such as changes in UAV trajectory.

@@

%--------------------------------------
\section{Conclusions}
\label{conclusions}
%--------------------------------------

>>>>

As already mentioned in section \ref{sec:model}, problems that are not directly related to code correctness may be tackled with formal methods, as long as the are conveniently modeled. Ara\'ujo {\it et. al} \cite{Araujo16} employed SMT for handling non-convex optimization problems, with the goal of ensuring optimal solutions. Indeed, it is possible to recursively re-constrains a model checking procedure, by using the current counterexample as a seed for the next run, until a global minimum is achieved. Nonetheless, the elapsed execution time is still a bottleneck for some applications, such as changes in UAV trajectory, but that can be improved, through the use of simplification techniques and and problem constraints.

@@

Regarding behavior correctness, many other applications can be tackled, such as the ones related to automatic classification. Amoedo {\it et. al} proposed a modulation classification methodology, which the goal of spectrum sensing for opportunistic transmissions. Given that 
%--------------------------------------
\section{Conclusions}
\label{conclusions}
%--------------------------------------
